Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-12-11 doc/_fitseq2_sim.qmd
small update to text

@fig-SIX_fitseq2(A) and (B) show the simulation's frequency and log frequency
ratio trajectories, respectively. Qualitatively, these results are very similar
to those shown in Fig. 1 of @li2023. As done throughout the main text,
@fig-SIX_fitseq2(C) shows examples of the posterior predictive checks for the
neutral lineages and a few of the mutant lineages. We can see that our inference
pipeline can fit this simulated data for the examples shown. Furthermore,
@fig-SIX_fitseq2(D) compares the ground truth fitness values and the inferred
parameters for all mutant lineages. @fig-SIX_fitseq2 shows the comparison
between the inference with the software provided in @li2023 and our inference
pipeline. We note that although the values are highly correlated, the scale of
the axis is very different.

>>>>

@fig-SIX_fitseq2(A) and (B) show the simulation's frequency and log frequency
ratio trajectories, respectively. Qualitatively, these results are very similar
to those shown in Fig. 1 of @li2023. As done throughout the main text,
@fig-SIX_fitseq2(C) shows examples of the posterior predictive checks for the
neutral lineages and a few of the mutant lineages. We can see that our inference
pipeline can fit this simulated data for the examples shown. Furthermore,
@fig-SIX_fitseq2(D) compares the ground truth fitness values and the inferred
parameters for all mutant lineages. @fig-SIX_fitseq2 shows the comparison
between the inference with the software provided in [@li2023] and our inference
pipeline. We note that although the values are highly correlated, the scale of
the axis is very different. This scale difference comes from the differences in
models used to infer the relative fitness value. While our model assumes an
exponential change in the relative frequency of the barcode, @li2023 works
directly with the number of cells rather than the relative frequency, assuming a
Malthusian fitness form. In other words, while our model is agnostic to the
underlying type of growth mechanism, as long as the condition of exponential
change in relative frequency is satisfied, @li2023 assumes exponential growth of
the number of cells, resulting in a discrepancy between the obtained numbers.
